Appendix to Public Gender Egalitarianism: A Dataset of Dynamic Comparative

### 2021-06-21 paper/pge_appendix.Rmd
fix dcpo_input_* for separate indices in Appendix C

dcpo_input_political <- DCPOtools::format_dcpo(dcpo_input_raw_public1,
                                            scale_q = "polileader4",
                                            scale_cp = 2)
save(dcpo_input_political, file = here::here("data", "dcpo_input_political.rda"))

dcpo_input_workplace <- DCPOtools::format_dcpo(dcpo_input_raw_public1,
                                            scale_q = "job3a",
                                            scale_cp = 2)
save(dcpo_input_workplace, file = here::here("data", "dcpo_input_workplace.rda"))

dcpo_input_education <- DCPOtools::format_dcpo(dcpo_input_raw_public1,
                                            scale_q = "education4",
                                            scale_cp = 2)
save(dcpo_input_education, file = here::here("data", "dcpo_input_education.rda"))
```

>>>>

dcpo_input_political <- DCPOtools::format_dcpo(dcpo_input_raw_political1,
                                            scale_q = "polileader4",
                                            scale_cp = 2)
save(dcpo_input_political, file = here::here("data", "dcpo_input_political.rda"))

dcpo_input_workplace <- DCPOtools::format_dcpo(dcpo_input_raw_workplace1,
                                            scale_q = "job3a",
                                            scale_cp = 2)
save(dcpo_input_workplace, file = here::here("data", "dcpo_input_workplace.rda"))

dcpo_input_education <- DCPOtools::format_dcpo(dcpo_input_raw_education1,
                                            scale_q = "education4",
                                            scale_cp = 2)
save(dcpo_input_education, file = here::here("data", "dcpo_input_education.rda"))
```
